---
title: "Alexander H. von Hafften - Teaching"
subtitle: "Ph.D. Student in Economics and Finance at UW-Madison"
---

```{r setup, echo = FALSE}
library(knitr)
```

:::: {style="display: grid; grid-template-columns: 1fr 5fr; grid-column-gap: 10px;"}


::: {}

```{r child ='sidebar_nav.Rmd'}
```

:::

::: {}

[Provide Anonymous Feedback](https://forms.gle/VwCe6dwtcH1CD1iC6)

#### ECON 712A Macroeconomic Theory (Fall 2021)

[Dean Corbae's Teaching Website](https://sites.google.com/a/wisc.edu/deancorbae/teaching)

Discussion Section Handouts:

- [Handout 1](https://vonhafften.github.io/handout_1.pdf) - Solutions

- Handout 2 - Solutions

- Handout 3 - Solutions

- Handout 4 - Solutions

- Handout 5 - Solutions

- Handout 6 - Solutions

- Handout 7 - Solutions

Problem Sets:

- Problem Set 1

- Problem Set 2

- Problem Set 3

- Problem Set 4

- Problem Set 5

- Problem Set 6

- Problem Set 7

#### Macro Preliminary Exams

[Past Prelim Questions](https://econ.wisc.edu/doctoral/preliminary-examinations/)

Unofficial Solutions

- [Previous 714B Exam Questions](https://vonhafften.github.io/econ714b_pastexamquestions.html)

- [Jason Choi](https://sites.google.com/site/jasonchoihj/teaching/prelim-2019?authuser=0)

- [Eirik Brandsaas](https://sites.google.com/site/eirikbrandsaas/teaching/prelim2018)

:::

::::